---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fastTS

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/petersonR/fastTS/branch/main/graph/badge.svg)](https://app.codecov.io/gh/petersonR/fastTS?branch=main)
[![R-CMD-check](https://github.com/petersonR/fastTS/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/petersonR/fastTS/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/fastTS)](https://CRAN.R-project.org/package=fastTS)
<!-- badges: end -->

## Overview

The `fastTS` package efficiently fits long, high-frequency time series with complex seasonality, even with a high-dimensional exogenous feature set. It implements the sparsity-ranked lasso (and similar methods) for time series data.

Originally described in [Peterson and Cavanaugh (2022)](https://doi.org/10.1007/s10182-021-00431-7) in the context of variable selection with interactions and/or polynomials, *ranked sparsity* is a philosophy of variable selection in the presence of prior informational asymmetry. 

In time series data with complex seasonality or exogenous features; see [Peterson and Cavanaugh (2023+)](https://doi.org/10.48550/arXiv.2211.01492), which also describes this package in greater detail. The basic premise is to utilize the sparsity-ranked lasso (or similar) to be less skeptical of more recent lags, and suspected seasonal relationships. 


## Installation

You can install the development version of `fastTS` like so:

```{r install, eval = FALSE}
# install.packages("remotes")
remotes::install_github("PetersonR/fastTS")
```

Or, install from CRAN with:

```{r install_cran, eval = FALSE}
install.packages("fastTS")
```

## Example

This is a basic example.

```{r example}
library(fastTS)

y <- cumsum(rnorm(100))
fit <- fastTS(y, gamma = c(0, .5))

fit
```

## Learn more

To learn more and to see this methodology in action, see: 

- [Simple case studies vignette](https://petersonr.github.io/fastTS/articles/case_studies.html)
- [Modeling hourly ER arrival data with complex seasonality](https://petersonr.github.io/fastTS/articles/hourly_er_visits.html)
- [Did Denver’s 2022 ‘Zero Fare for Cleaner Air’ campaign actually work?](https://data-diction.com/posts/did-denver-zero-fare-policy-work/#modeling)
