---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# srlTS

<!-- badges: start -->
[![R-CMD-check](https://github.com/petersonR/srlTS/workflows/R-CMD-check/badge.svg)](https://github.com/petersonR/srlTS/actions)
[![Codecov test coverage](https://codecov.io/gh/petersonR/srlTS/branch/main/graph/badge.svg)](https://app.codecov.io/gh/petersonR/srlTS?branch=main)
<!-- badges: end -->

The goal of srlTS is to fit the sparsity-ranked lasso to time series data. 

## Installation

You can install the development version of srlTS like so:

```{r install, eval = FALSE}
# install.packages("remotes")
remotes::install_github("PetersonR/srlTS")
```

## Examples

This is a basic example.

```{r example}
library(srlTS)

y <- cumsum(rnorm(100))
fit <- srlTS(y, gamma = c(0, .5))

fit
```

For the Lake Huron data set

```{r lakehuron}
data("LakeHuron")

fit_LH <- srlTS(LakeHuron)

fit_LH
coef(fit_LH)
```

If you have a univariate time series with suspected trend, such as the EuStockMarkets data set,

```{r stocks}
data("EuStockMarkets")
X <- as.numeric(time(EuStockMarkets))
X_sp <- splines::bs(X-min(X), df = 9)

fit_stock <- srlTS(log(EuStockMarkets[,1]), n_lags_max = 400, X = X_sp, w_exo = "unpenalized")
tail(coef(fit_stock), 11)

# insert plot? 
```

If you have a univariate time series with suspected trend, such as the airquality data set,

```{r seasonal}
data("nottem")
fit_nt <- srlTS(nottem, n_lags_max = 24)
coef(fit_nt)

data("UKDriverDeaths")
fit_ukdd <- srlTS(UKDriverDeaths, n_lags_max = 24)
coef(fit_ukdd)

# Show how to add holiday indicators?

data("sunspot.month")
fit_ssm <- srlTS(sunspot.month)
fit_ssm
summary(fit_ssm$relaxed_fit)
```

